Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-08-28 paper.tex
Add Game Theory Description

\begin{document}
%
\title{Decentralized Data Marketplace to Enable Trusted Machine Economy}
%
\author{
%%% Fill in name here
\IEEEauthorblockN{Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}, Ching-Hua Lin\IEEEauthorrefmark{2}, Zan-Jun Wang\IEEEauthorrefmark{3}}\\

@@

%%% Fill in email here
\IEEEauthorblockA{\IEEEauthorrefmark{1}jserv@ccns.ncku.edu.tw, \IEEEauthorrefmark{2}jkrvivian@gmail.com, \IEEEauthorrefmark{3}twzjwang@gmail.com}
}

@@

@@

\section{System Architecture}
\subsection{Participants}
There are four major roles in the decentralized data marketplace.

@@

@@

\subsection{Participants Registration}
At the beginning, the registrar creates a Registration Contact, which maintains all participants' information, including their DID (Decentralized Identifiers) information and public keys. Then some preselected brokers who are trustworthy are added to the decentralized data marketplace. Anyone who would like to sell or purchase data may register to become the data providers or consumers. The registrar has the authority to agree with applications.

\subsection{Launching and Searching Products}
To sell the sensing data, a data provider has to launch a new product on the data marketplace in advance. The data provider determines a trusted broker and asks the broker to create a new MAM channel and Product Contract.

Brokers certify session keys as well. However, it is a risk revealing session keys to brokers since contents may be copied by brokers, which causes data providers' loss. Therefore, Blind signature is used to prevent the situation. When a data provider asks a broker to ceritfy new session key, the data provider uses the broker's public key, which is available in the Registration Contact after the broker's registration, as a blinding factor, and the session key is blinded. Then the data provider sends the blinded session key to the broker. The broker signs the message and returns the signature to data provider. The data provider removes the blinding factor and obtains the broker's signature of the session key. Only one session key can be signed in each product, so data providers can't fake a session key to deceive consumers.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{key_certification}
	\caption{Session key certification with blind signature}
	\label{fig:key_certification}
\end{figure}

@@

\subsection{Trading}
Once a consumer who want to subscribe the sensor data pays a subscription fee to the Product Contract, it is added to the subscriber list automatically by the smart contract. To decrypt the streaming data on the MAM channel, session key should be exchanged between data provider and consumers. The data provider requests the subscription list maintained by the Product Contract and obtains accounts of each subscriber. After that, the data provider can also get public keys of each subscriber from the Registration Contact with their accounts. For each subscriber, the data provider encrypts the session key and broker's signature with the subscriber's public key and sends the ciphertext to the Product Contract. Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to get the session key and signature. Consumers can obtain the broker's public key on the Registration Contact as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker. Afterward, encrypted sensing data is uploaded to the MAM channel, and consumers can download and decrypt them with the session¸

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{key_exchange}
	\caption{Session key exchange between the data provider and consumer}
	\label{fig:key_exchange}
\end{figure}

\subsection{Refunding}
It is probable that the sensor is malfunctioning after the consumers pay the subscription fee. To protect consumers' right, the subscription fee are not transfered to the data provider until all data is generated and uploaded to the MAM channel. If the expected data is not available, consumers can ask for refunds. We assume that less than half of consumers in the Product Contract are irrational and malicious. Each subscriber can vote for refunding at any time. If the ratio of consent votes of refunding is higher than the $threshold$ at $k$th data samples, the subscription fee is proportionally transfered to the data provider, broker and every subscriber. The subscription fee can be prorated as below:

@@

Where $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ is the brokerage fee(\%), $F_{t}$ is the transaction fee of the smart contract(\%), $N$ is the number of subscribers in this contract.

>>>>

\begin{document}
%
\title{Decentralized Data Marketplace to Enable Trusted Machine Economy}
%
\author{
%%% Fill in name here
\IEEEauthorblockN{Zan-Jun Wang\IEEEauthorrefmark{3}, Ching-Hua Lin\IEEEauthorrefmark{2}, Yang-Hao Yuan\IEEEauthorrefmark{4}, Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}}\\

@@

%%% Fill in email here
\IEEEauthorblockA{\IEEEauthorrefmark{1}jserv@ccns.ncku.edu.tw, \IEEEauthorrefmark{2}jkrvivian@gmail.com, \IEEEauthorrefmark{3}twzjwang@gmail.com, \IEEEauthorrefmark{4}yanghau@biilabs.io}
}

@@

The authors want to ensure the sustainability of decentralized data marketplace. The utility structure of IoT econimic system and game theory models are presented in the work of Dusit Niyato et al.\cite{UtilityStruct}. Game theory provides a mathematical solution to proof the existence of Nash Equilibrium in IoT economy. data marketplace organizers can apply numerical analysis on game theory, which would help them to find out their optimal pofit.

@@

\section{System Architecture}
\subsection{Participants}
There are four major roles in the decentralized data marketplace (Figure \ref{fig:system_design}).

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.4\textwidth]{system_design}
	\caption{System Design.}
	\label{fig:system_design}
\end{figure}

@@

In our game theory model there are two kinds of players. One is data provider, and the other one is data buyer. Data provider would receive subscription fee for buying data each time the data is transmitted to data buyer.
The data buyer will keep buying data from data povider, only when the data sold by the data provider with high enough correct rate, $\pi_{correct}$. We deonte this correct rate threshold with $\pi_{threshold}$.
Once the correct rate is lower than $\pi_{threshold}$, the data buyers would consider this data provider as a malicious data provider, and reject to buy the data from this data provider.

\subsection{Participants Registration}
At the beginning, the registrar creates a Registration Contract (Figure \ref{fig:registration_contract}), which maintains all participants' information, including their DID (Decentralized Identifiers) Documents and public keys. Then some trustworthy brokers who pass procedures for conformity assessment are added to the decentralized data marketplace. Anyone who would like to sell or purchase data may register to become the data providers or consumers. The registrar has the authority to agree with applications.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.4\textwidth]{registration_contract}
	\caption{Registration Contract.}
	\label{fig:registration_contract}
\end{figure}

\subsection{Launching and Searching Products}
To sell the sensing data, a data provider has to launch a new product on the data marketplace in advance. The data provider determines a trusted broker and asks the broker to create a new MAM channel and Product Contract (Figure \ref{fig:product_contract}).

\begin{figure}[h]
\centering
\includegraphics[width=0.4\textwidth]{product_contract}
\caption{Product Contract.}
\label{fig:product_contract}
\end{figure}

Brokers certify session keys as well. However, it is a risk revealing session keys to brokers since contents may be copied by brokers, which causes data providers' loss. Therefore, Blind signature is used to prevent the situation. Figure \ref{fig:key_certification} shows the certification process. When a data provider asks a broker to ceritfy new session key, the data provider uses the broker's public key, which is available in the Registration Contract after the broker's registration, as a blinding factor, and the session key is blinded. Then the data provider sends the blinded session key to the broker. The broker signs the message and returns the signature to data provider. The data provider removes the blinding factor and obtains the broker's signature of the session key. Only one session key can be signed in each product, so data providers can't fake a session key to deceive consumers.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{key_certification}
	\caption{Session key certification process with blind signature.}
	\label{fig:key_certification}
\end{figure}

@@

\subsection{Trading}
Once a consumer who want to subscribe the sensor data pays a subscription fee to the Product Contract, it is added to the consumer list automatically by the smart contract. To decrypt the streaming data on the MAM channel, session key should be exchanged between data provider and consumers as shown in Figure \ref{fig:key_exchange}. The data provider requests the subscription list maintained by the Product Contract and obtains accounts of each consumer. After that, the data provider can also get public keys of each consumer from the Registration Contract with their accounts. For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext to the Product Contract. Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to get the session key and signature. Consumers can obtain the broker's public key on the Registration Contract as well, so they can verify that the signature is valid and the session key is the only one that is certified by the broker. Afterward, encrypted sensing data is uploaded to the MAM channel, and consumers can download and decrypt them with the session key.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{key_exchange}
	\caption{Session key exchange process between the data provider and consumer.}
	\label{fig:key_exchange}
\end{figure}

\subsection{Refunding}
It is probable that the sensor is malfunctioning after the consumers pay the subscription fee. To protect consumers' right, the subscription fee are not transfered to the data provider until all data is generated and uploaded to the MAM channel. If the expected data is not available, consumers can ask for refunds. We assume that less than half of consumers in the Product Contract are irrational and malicious. Each consumer can vote for refunding at any time. If the ratio of consent votes of refunding is higher than the $threshold$ at $k$th piece of data, the subscription fee is proportionally transfered to the data provider, broker and every consumer. The subscription fee can be prorated as below:

@@

where $price$  is the subscription price, $M$ is the number of expected data samples, $F_{b}$ is the brokerage fee(\%), $F_{t}$ is the transaction fee of the smart contract(\%), $N$ is the number of consumers in this contract.

To refund or withdraw subscription fee from the smart contract, data provider, broker, and consumer send a transaction to execute the smart contract and are responsible for transaction fee. We assume that only a half of the expected records are uploaded to the MAM channel. For the data provider and broker, they can withdraw a half of total subscription fee from the smart contract and $F_{b}$ \% belongs to the broker while the remaining belongs to the data provider. For consumers, they can get a half refund which should be deducted the transaction fee.

\subsection{Game Theory Evaluation}

\subsubsection{Model Description}
Repeated game consists of serveral repetitions of some stage games. In each stage game, the action player takes will effect the actions that players are going to take in the future stages. Repeated game can be illustrated with a decision tree and described their payoff with discounted sum of payoff. Discounted sum of payoff can capture the idea that what the players truly pursue is the sum of payoff in all stages and payoff in different stages may varify.

We use a repeated game to express the scenario of our Data Marketplace. Figure.\ref{fig:decision_tree} shows the decision tree to depict the the repeated game we used. Each level in this decision tree represents each round of data transmission from data provider to data buyers, and the data buyers would pay $p_{fee}$ in total to buy the data.

\begin{figure} \centering \includegraphics[width=3.3in]{img/decision_tree.png} \caption{Decision Tree}
    \label{fig:decision_tree} \end{figure}
For every $n$ round, the data provider would cost $C_{maintain}$ to maintain or enhance the sensors that data provider owns. We call this as a maintain period. Moreover, the value of data and the cost of maintenance will decrease as time pass, so we introduce a discount factor $\beta$ to depict this phenomena.

We have these following assumptions:
\begin{itemize}
\item  There is no any other data providers provide the same product in Data Marketplace. Therefore, we can consider each provider's behavior independently. That means this decision tree represent the behavior of only one data provider.
\item  More than 51\% of data buyers are amoung complete information exchange state. In other words, once one of them launches voting for stopping buying data and refunding, they would succeed in refund voting.
\item  One of the data buyers who has complete imformation exchange with other 51\% buyers will definitely find out the wrong or fake data provided by data provider is wrong.
\end{itemize}

Based on the description above, the discount sum of payoff for our repeated game is 
\begin{equation} \label{payoff}
\sum_{i=0}^{m}{\beta^{in}\cdot [(\sum_{j=0}^{n} \beta^j \cdot p_{fee}) - C_{maintain}]}
\end{equation}

Al-Fagih et al. presented\cite{DataPrice} $p_{fee}$ is a sigmoid function of $\pi_{correct}$, and based on rule of thumb $C_{maintain}$ is about a exponential function of $\pi_{correct}$. We can substitute $p_{fee}$ and $C_{maintain}$ with $\pi_{correct}$ into Eq. (\ref{payoff}), then we can find out the Nash Equilibrium of repeated game with differential easily.
